\chapter{Introduction}

This is a story I've told time and time again, but not to you or anyone I know.
Just to myself.
I have written and rewritten it more times than I can count and have decided that now is the time to share it.
So here it goes...

A few years ago, there was a young woman named Sophia.
She had just finished high school and was ready to start her new college life, but she could not afford rent on her own and instead needed to stay with her grandfather Ahab, a retired professor at the university she wanted to attend.
He was too old to take care of himself anymore, so they had a simple arrangement: she would take care of chores around the house and would be given a room in exchange.

After returning home from freshman orientation, she decided to start dinner early.
While in the kitchen looking for ingredients, she raised her voice for Ahab to hear, ``Grampa, would you like anything in particular for dinner?''

No response.
She shrugged, thinking he was napping in the bedroom and began pulling out some pasta and tomatoes to make some Italian food.
She again called out, ``I'll be making Spaghetti, that OK?''

Again, there was no response, so she began preparing everything.
After everything was ready, she checked the master bedroom to see if Ahab was there.
He was not.

Confused, she began looking all over, but couldn't find him.
She then checked the driveway to make sure his car was still there.
After a few more minutes of increasingly frantic searching, she found a door that was slightly ajar.
Before that moment, she had never opened the door and simply assumed that it was closet or a pantry of some sort.

When she opened it, she was greeted by a rather steep flight of stairs. ``Grampa!'' She called again, ``Are you up there?''

Again, no response, but her curiosity got the better of her.
At the top of the stairs, there was yet another door, but it was closed this time.
She knocked, ``Grampa, are you in there?''

``Ah.'' She heard a gruff, but familiar voice, ``Yeah. Come in.''

When she opened the door, she found a large library, with the walls completely filled with a huge number of books of all different shapes and sizes.
On the far side of the room was a large window looking out onto a tumultuous sky illuminating two tall chairs with an end-table in-between, where a cold, stained cup of coffee rested.
The chairs were facing away from Sophia, so she couldn't quite see Ahab, but knew he was sitting in one of them.

She took a step forward and inspected the nearest shelf, which was about shoulder-height. It was filled with titles she had never seen before:

\begin{itemize}
\item The Essence Series
\item The Arcane Algorithm Archive
\item Sufficiently Advanced Technology
\end{itemize}

She mindlessly pulled out a book at random before walking to the chairs, only to find Ahab gazing at the sky with a stern expression.
She then said, ``Hey Grampa, I didn't know you liked reading so much.''

He looked up and took a deep breath before again looking towards the window, ``Yeah. I used to read a bit when my eyesight was better.''

Sophia laughed a bit and took the open chair before inspecting the book in her hands.
It was a simple black book and the spine read, \emph{A Patchwork Quilt}.
Outside of the title, there was nothing else on the cover.
Curious, Sophia asked, ``Wait. Who wrote this? There is no author information.''

Ahab again sighed. ``I did, in a way. I kinda wrote all of these.''

Shocked, Sophia looked around.
There must have been hundreds of books, maybe even thousands. ``Wait. You wrote all of these? That's incredible.''

``It's not what you think. Open it.'' He looked over and tapped the book in Sophia's hand.

She did so, only to find every page blank.
After a few seconds, she said, ``I don't understand.''

``These books are all of my failed creations. Ideas I had throughout the years but never finished, some of them I never even started. Now I'm too old to work on any of them.'' With that, Ahab again began staring into space.

Sophia didn't say anything either for a while, but instead stood and began inspecting the titles.
She then put her book back before saying, ``I guess the reason there is no author information is because they haven't technically been written yet?''

``Yeah.'' Ahab said. Sophia could not see him from behind the chair, but could hear the defeat in his voice.
``I tried. I really did. I wrote for years and years, but never published a single thing. Something more important always came up. Now, these stories will die with me.''

Again Sophia did not respond immediately, but instead knelt down to one of the bottom rows of books and felt the spine of one entitled, \emph{Inanimate}.
Like before, it was a solid color without any indicating marks except for the title.
She then pulled it out and thumped it against her palm before saying, ``How about you tell me about one of them over dinner. C'mon, let's go eat. I'll grab a pen.''

\emph{This is the story of Sophia and Ahab told through their writing.}