\chapter{The Immortal Lich}

I am not a philosopher, but I have always found the human mind to be an interesting and complex concept that has been a topic of intense debate since humans learned of its existence.
Nowadays, most people generally believe that the mind is a complex amalgamation of thoughts, feelings, and perceptions, all of which are processed within the human brain.
I absolutely agree with this, but I also feel it is important to consider the human mind as more than just a metaphysical representation of the brain.

Have you ever argued with someone who has a completely different worldview?
You might argue your point, confident that you are absolutely correct based on your own set of facts and logic, but no matter how hard you try, you cannot persuade the other person.
You might start by making a somewhat innocuous claim, and they would question how you could have such an absurd opinion.
From there, you might provide facts and figures to support your idea, but to no avail.
Your opponent will continually dance around the truth by asking unrelated questions or disputing common knowledge.
At some point, after potentially hours of bickering between the two of you, you might claim that the other person has "lost their mind."

And they have, to some extent.
Biologically, you have brains of roughly the same size, but the neurons are connected differently.
This leads to radically different minds.

To me, the mind is more or less the philosophical world a person lives in.
Proper conversation can only happen when two people live close enough together to actually talk properly to one another.
Otherwise, everyone is just shouting into the void and hoping the other person can hear them.

This is why whenever I start a conversation, I try to ask a series of somewhat fundamental questions.
These questions allow me to draw a mental map from my mind to theirs in order to better facilitate conversation.
Without these questions, discussions turn into debates, and debates into arguments.
No one listens in an argument.
They are a waste of time.

